Supporting Information

### 2017-02-09 portfolio/text/supp.Rnw
Text edits
Integrate main species into supplemental table

% TODO: Are you saying that PWS sockeye permits were combined with BB sockeye permits?I can't remember but that's what it sounds like so I just wanted to be clear.

@@

\begin{table}[h!]
\footnotesize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes.}
  \label{tab:strategies}
  \begin{tabular}{lll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

>>>>

@@

\begin{table}[h!]
\scriptsize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. The column ``Main species'' indicates species that make up at
least 10\% of the total revenue across all years and individuals for that
fishing strategy. ``Sock'' refers to sockeye salmon.}
  \label{tab:strategies}
  \begin{tabular}{llll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}
